% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science, version 1.1
\documentstyle{llncs}
%
\begin{document}

\title{Comparação de métodos de classificação}

\author{Augusto Ribas\inst{1}, Bruno Nazário\inst{1} e Doglas Sorgatto\inst{1}}

\institute{Faculdade de Computação - Universidade Federal de Mato Grosso do Sul}

\maketitle

\begin{abstract}
Avaliamos o desempenho de três métodos classificação.
\end{abstract}
%
\section{Introduçao}

Exemplo de citaçao  \cite{clar:eke}
\section{Material e Metodos}
\section{Resultados e Discussao}


%
% ---- Bibliography ----
%
\begin{thebibliography}{5}
%
\bibitem {clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. {\bf 78} (1982) 315--333
%
\bibitem {clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris {\bf 287} (1978) 1013--1015
%
\bibitem {mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. {\bf 72} (1988) 28--55
%
\bibitem {tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)
%
\bibitem {rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. {\bf 33} (1980) 609--633
\end{thebibliography}
%
\end{document}
